A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-06-23 refl_maths/paper.tex
better plot and words

>>>>

Figure~\ref{fig:rough} shows the effect that increasing roughness can have on the scattering length density of some system, in this case \ce{D2O} on a silicon substrate. 
Notice that as the roughness gets to values similar to half the layer thickness, artifacts appear in the scattering length density profile. 
Below, where the roughness is too large, the scattering length density is less then the substrate scattering length density. 
This is unphysical, and indicates at an important factor that we should try and account for by not allowing large roughnesses with respect to the layer thickness, a common rule of thumb is to use less than one quarter. 
%
\begin{figure}[t]
    \includegraphics[width=0.49\textwidth]{roughness}
    \caption{The effect of a roughness greater than a given layer's thickness on the scattering length density profile. The layer thickness is \SI{10}{\angstrom}. The scattering length densities are those of \ce{D2O} on a atomically flat silicon. The roughness of the water layer is varied from \SI{3}{\angstrom} (blue), through \SI{5}{\angstrom} (orange), to \SI{7}{\angstrom} (green). The full scattering length density profile is given in (a), while (b) represents a zoomed in representation.}
    \label{fig:rough}
\end{figure}
%
